R for Clinical Study Reports and Submission

### 2023-07-09 index.qmd
update index.qmd

The [ICH E3: Structure and Content of Clinical Study Reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf)
provides robust guidance to sponsors for developing a CSR.
This book demystifies the complexity by guiding you on how to use R for
streamlining the preparation of CSRs. Moreover, it walks you through the
process of preparing the submission to regulatory agencies. Regardless of your
expertise level in R programming, this book serves as an essential resource
in your statistical programming toolkit, enhancing efficiency and accuracy
in clinical trials reporting.

@@

```{r, echo=FALSE}
knitr::kable(read.table("events.tsv", stringsAsFactors = FALSE, header = TRUE, sep = "\t"))
```

>>>>

The [ICH E3: Structure and Content of Clinical Study Reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf)
offer comprehensive instructions to sponsors on the creation of a CSR.
This book is a clear and straightforward guide on using R to streamline the process of preparing CSRs. Additionally, it provides detailed guidance on the submission process to regulatory agencies. Whether you are a beginner or an experienced R programmer, this book is an indispensable asset in your clinical reporting arsenal.

@@

```{r, echo=FALSE}
knitr::kable(
  read.table("events.tsv", 
             stringsAsFactors = FALSE, 
             header = TRUE, 
             sep = "\t")
  )
```
